Commit Rater

### 2015-09-25 presentations/paper/results.tex
Link to boxplots in Results

The boxplots for the other criteria are available in our Git and were not included here in order to save space.

>>>>

The boxplots for the other criteria are available in our Git\footnote{\url{https://github.com/hartenfels/Commit-Rater/tree/master/analysis/boxplots}} and were not included here in order to save space.
